%-------------------------
% Resume in Latex
% Based on: https://github.com/sb2nov/resume
% and Jake Gutierrez's version of it
% at https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% inspired by https://practicaltypography.com/resumes.html
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\input{preamble.tex}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

{\basictitle \Huge Nicholas Tapp-Hughes}

% Links

\vspace{2mm}
\footnotesize{
\href{https://www.nicholastapphughes.com}{nicholastapphughes.com} $|$
\hspace{-2mm}
\href{mailto:nicholas.tapphughes@gmail.com}{
    nicholas.tapphughes@gmail.com} $|$
\hspace{-2mm}
\href{https://www.linkedin.com/in/nicholas-tapp-hughes/}{
    linkedin.com/in/nicholas-tapp-hughes} $|$
\hspace{-2mm}
\href{https://github.com/tapphughesn}{
    github.com/tapphughesn}
}

% Mission Statement
% Commenting out for now, Google doesn't like mission statements and I don't think other places like them either

\small
\vspace{2mm}
% \textbf{Full-Stack Engineer} focused on building high-quality, scalable, and trustworthy AI, web, and data applications that meet stakeholder needs. Experienced in working directly with end users on ambiguous problems to deliver solutions.

%-----------EXPERIENCE-----------
\vspace{-4mm}
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \vspace{-1mm}
    \resumeSubheading
      {Epic Systems Corporation}{July 2023--July 2025}
      {Software Developer}{}
      \vspace{-1mm}
      
      \resumeItemListStart

        \resumeItem{Improved screening follow-up workflows for 80+ hospital systems (driven by customer feature requests) by architecting a configurable system that enables automatic follow-up care suggestions based on screening insights.}
        
        \resumeItem{Led migration of 2 radiology workflows from VB to .NET/C\# and React, delivering UX enhancements and a 20\% performance improvement.}

        \resumeItem{Contributed technical designs and solicited customer feedback for an LLM-extracted clinical insights feature as part of a broader project that resulted in earlier diagnosis for 70\% of lung cancer cases at The Christ Hospital.}

        \resumeItem{Shipped 62 bug fixes to 500+ healthcare systems by tracing logs and diagnosing issues across the full stack.}

        % The following 3 points are more for a generalist software eng role
        \resumeItem{Collected feedback/pain points, built trust, and facilitated installs during 20 days spent on-site with end users.}

        \resumeItem{Ensured reliability and maintainability by using test suites, analyzing performance, and favoring simple design.}

        \resumeItem{Built front-end React applications that are accessible to non-sighted users and available in 9+ languages.}

      \resumeItemListEnd

      \resumeSubheading
      {UNC Gillings School of Global Public Health}{Aug 2021--Jun 2025}
      {Graduate Research Assistant}{}
      \vspace{-1mm}
      
      \resumeItemListStart

        \resumeItem{Improved policymakers' understanding of smoking behavior in the US adult population by building a microsimulation model that predicts year-over-year smoking behavior at the individual level.}

        \resumeItem{Accelerated the project team's productivity and synchronization by maintaining the codebase, building robust data pipelines, sharing regular results, recommending technologies, and onboarding new people.}

        \resumeItem{Published a paper in PLoS One: \href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0342083}{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0342083}.}

      \resumeItemListEnd

    \resumeSubheading
      {UNC Dept. of Computer Science}{Aug 2021--May 2023}
      {Graduate Researcher (Master's Degree)}{}
      \vspace{-1mm}
      
      \resumeItemListStart
        \resumeItem{Coinvented and implemented (in \CC \hspace{1pt} and Python) an algorithm for extracting salient features from 3D mesh objects by finding an optimally-fitting skeletal representation given the differential geometric properties of the object.}

        \resumeItem{Achieved a 22\% improvement in autism classification accuracy on a hippocampus dataset via new method.}

        \resumeItem{Published a paper in the Journal of Mathematical Imaging and Vision: \href{https://rdcu.be/eFX0G}{https://rdcu.be/eFX0G}.}
        
      \resumeItemListEnd

    \resumeSubheading
      {Sila Nanotechnologies Inc.}{Jun 2022--Aug 2022}
      {Software Engineering R\&D Intern}{}
      \vspace{-1mm}
      
      \resumeItemListStart
        \resumeItem{Enhanced a computer vision pipeline for evaluating lithium-ion battery swelling; improved measurement accuracy by $\sim$20\% and consulted on development strategy.}

      \resumeItemListEnd

    \resumeSubheading
      {Kitware Inc.}{June 2021--Aug 2021}
      {Medical Computing R\&D Intern}{}
      \vspace{-1mm}
      
      \resumeItemListStart
        \resumeItem{Prototyped a mobile application to support Point-of-Care Ultrasound funded by DARPA.}

        \resumeItem{Developed a computer vision pipeline with custom Python video processing algorithms and curated neural network models to do anatomy reconstruction and prediction of pneumothorax. }
        
      \resumeItemListEnd
      
      
     \resumeSubHeadingListEnd

%-----------Projects-----------
\vspace{-6mm}
\section{PROJECTS}
  \resumeSubHeadingListStart

    % \vspace{-1.5mm} 
    % \resumeSubheading
    %   {Automated Follow-Up Suggestions for Screening Procedures}{}{}{}
    %   \vspace{-5mm}
    %   \resumeNoLabelItemListStart
    %     \resumeItem{A system for automatically suggesting follow-up care based on insights from screening exams (e.g. for breast/lung/colon/cervical cancer) or general radiology. Suggestions are flexibly configured by hospital administrators based on the type of screening and its findings.}
    %   \resumeNoLabelItemListEnd

    % \vspace{-1.5mm}
    % \resumeSubheading
    %   {{\href{https://rdcu.be/eFX0G}{Evolutionary Skeletal Representations Algorithm}}}{2021--2023}{}{}
    %   \vspace{-4mm}
    %   \resumeNoLabelItemListStart
    %     \resumeItem{\footnotesize An algorithm for determining salient statistical features of 3D mesh objects using skeletal representations and differential geometric processing. Implemented with Python, \CC, and shell scripts. Published in JMIV and released as open-source.} 
    %   \resumeNoLabelItemListEnd

    % \vspace{-1.5mm} 
    % \resumeSubheading
    %   {{\href{https://github.com/tapphughesn/menthol-model}{Smoking Behavior Microsimulation Model}}}{2021--2025}{}{}
    %   \vspace{-4mm}
    %   \resumeNoLabelItemListStart
    %     \resumeItem{\footnotesize A simulation of individual lifetime smoking behavior for the entire US adult population, built with Python.
    %     Based on a 2\textsuperscript{nd}-order Markov chain multinomial logistic regression model.
    %     Predicts smoking behavior, mortality, and incidence of disease based on individual and societal factors. Accompanied by large-scale orchestration and data analysis.}
    %   \resumeNoLabelItemListEnd

    \vspace{-1.5mm}
    \resumeSubheading
      {{\href{https://github.com/tapphughesn/netseg}{NetSeg}}}{2020--2022}{}{}
      \vspace{-4mm}
      \resumeNoLabelItemListStart
        \resumeItem{
        A 3D convolutional neural network that I architected and trained using TensorFlow to segment subcortical brain structures in MR images. I created custom data preprocessing steps, loss functions, and a CLI and GUI wrapper.}
      \resumeNoLabelItemListEnd
      
    \resumeSubheading
      {{\href{https://github.com/tapphughesn/blog}{Blog Engine}}}{2025--Present}{}{}
      \vspace{-4mm}
      \resumeNoLabelItemListStart
        \resumeItem{A personal website and blog engine that I built using React and hosted on AWS/Cloudflare. 
        I used an Amplify/DynamoDB/Lambda/SES cloud stack + Python/Bash scripting to support verified subscribers, automatically convert Google Docs with custom components to blog posts, and mitigate security risks such as email enumeration and DoS. 
        I leverage my background in math and computer science to write about technical topics (such as Buffon's Needle Problem) in rich and interactive blog posts.}
      \resumeNoLabelItemListEnd

  \vspace{-2mm}
  \resumeSubHeadingListEnd
      
     
 %-----------Publications-----------
% \vspace{-6mm}
% \section{PUBLICATIONS}
% \vspace{-1mm} 
%
% \resumeItemListStart
%
%     \resumeItem{\footnotesize Pizer, S. M., Liu, Z., Zhao, J., \textbf{Tapp-Hughes, N.}, Damon, J., Zhang, M., Marron, J. S., Taheri, M., Vicory, J., \textit{Interior Object Geometry via Fitted Frames}, Journal of Mathematical Imaging and Vision. Available: \href{https://rdcu.be/eFX0G}{https://rdcu.be/eFX0G}.}
%
%     \resumeItem{\footnotesize Mills, S. D., \textbf{Tapp-Hughes, N.}, Zhang, Y., Ribisl, K. M., Wiesen, C. A., Fan, J., Hassmiller Lich, K., \textit{Development and Validation of the TwIST Model}, PLoS One. Available: \href{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0342083}{https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0342083}.}
%         
%     % \resumeItem{Mills, S. D., \textbf{Tapp-Hughes, N.}, Zhang, Y., Ribisl, K. M., Wiesen, C. A., \& Hassmiller Lich, K., \textit{The impact of a menthol cigarette ban on tobacco use, lung cancer, and life expectancy}, Poster presentation at the annual meeting of the Society for Research on Nicotine or Tobacco, Baltimore, MD.}
%
%     % \resumeItem{\textbf{Nicholas Tapp-Hughes}, \textit{A 3d U-net for Segmentation of Subcortical Structures In MR Images of 12 and 24 Month-old Infants}, Available: Carolina Digital Repository, \href{https://cdr.lib.unc.edu/concern/honors_theses/4f16c8286}{https://cdr.lib.unc.edu/concern/honors\_theses/4f16c8286}.}
%     
% \resumeItemListEnd

%-----------SKILLS-----------
\vspace{-4mm}
\section{SKILLS}
\vspace{-2mm}
  \small{
    \textbf{Languages:}{ Python, TypeScript, \CC, Java, C\#, SQL, Rust, Lua, Bash} \\
    \textbf{Frameworks:}{ AWS, .NET, React, SQL Server, Testing, Debugging, Build Systems, Containerization, Package Managers } \\
    \textbf{Other:}{ Machine Learning Research, Software Development Lifecycle, Linux, System Design, LLMs, Agile, Open Source}
  }

%-----------EDUCATION-----------
\vspace{-4mm}
\section{EDUCATION}
  \resumeSubHeadingListStart
        \vspace{-1.5mm} 
    \resumeSubheading
        {University of North Carolina at Chapel Hill}{}
      % {B.S. Applied Mathematics, Computer Science with Honors}{Aug 2017--May 2021}
        {}{}
      \vspace{-8pt} 
  \item

    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{ \hspace{-2mm} \small M.S. Computer Science} & \textit{ \small Aug 2021--May 2023} \\
    \end{tabular*}


\item \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{ \hspace{-2mm} \small B.S. Applied Mathematics and Computer Science with Honors and Highest Distinction} & \textit{ \small Aug 2017--May 2021} \\
    \end{tabular*}

      \resumeItemListStart
      
        % \resumeItem{Cumulative GPA: 3.92/4, \hspace{1mm} Math GPA: 3.87/4, \hspace{1mm} CS GPA: 3.97/4}

        \vspace{-3mm} \resumeItem{GPA: 3.92/4}

      \resumeItemListEnd
      
      
      \vspace{-5mm}
      
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
